---
title: "Musculoskeletal Network Experimentation in R"
author: "Sean Collins"
date: "1/29/2017"
output: html_document
---

```{r setup, include=FALSE, error=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Musculoskeletal Network Experimentation in R

Just a notebook to do some experimentation in R for the construction and analysis of anatomical / musculoskeletal networks.

Learning to use R for graph analysis through the book:
Højsgaard, Søren; Edwards, David; Lauritzen, Steffen (2012-02-22). Graphical Models with R (Use R!) (Kindle Location 292). Springer New York.


```{r load packages, echo=FALSE}
library(gRbase)
library(Rgraphviz)
library(igraph)
```

## Load Upper Extremity Anatomical Network

```{r load and convert}
#Load csv file which is an adjacency matrix
ue<-read.csv("AdultForeLimb.csv",row.names = 1, header= TRUE)
#Convert dataframe to a matrix
aue<-as.matrix(ue)
iue<-graph_from_adjacency_matrix(aue, mode = "undirected")
gue<-as_graphnel(iue)


x<-as(aue,"graphNEL", "undirected")

```

```{r load and convert}
#Load csv file which is an adjacency matrix
ue<-read.csv("AdultForeLimb.csv",row.names = 1, header= TRUE)
#Convert dataframe to a matrix
aue<-as.matrix(ue)
iue<-graph_from_adjacency_matrix(aue, mode = "undirected")
gue<-as_graphnel(iue)
```



